---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  eval = FALSE
)
```

# twittercache

<!-- badges: start -->
<!-- badges: end -->

`twittercache` facilitates robust sampling of the Twitter network. The basic idea is to save any data into a local cache as you as you get it. `twittercache` is build on top of [`rtweet`](http://rtweet.info/).

## NAMES

- request queue
- failure log

## Installation

You can install the development version of `twittercache` with:

``` r
install.packages("devtools")
devtools::install_github("alexpghayes/twittercache")
```

`twittercache` is not on CRAN and I don't plan to submit it.

## Step 1: Register your tokens

Create a token with `rtweet` and then register it with `register_token()`:

```{r eval = FALSE}
library(twittercache)

token <- rtweet::create_token(
  app = "FILL_THIS_IN",
  consumer_key = "FILL_THIS_IN",
  consumer_secret = "FILL_THIS_IN",
  access_token = "FILL_THIS_IN",
  access_secret = "FILL_THIS_IN"
)

register_token(token)
```

Or add existing `rtweet` tokens with `get_token()` / `get_tokens()`:

```{r}
token <- get_token()
register_token(token)
```

`twittercache` is smart and only allows you to register a token once, so don't worry about accidentally registering the same token multiple times:

```{r}
register_token(token)
```

Check how many tokens you have registered with

```{r}
get_number_of_tokens()
```

## Step 2: Request information on nodes in the twitter graph

Request information on a nodes with `request()`:

```{r}
request("alexpghayes")
```

You can pass either screen names or user IDs to `request()`:

```{r}
library(rtweet)

rohe_lab <- c("alexpghayes", "karlrohe", "krauskae", "_fchen",
              "JosephineLukito", "yinizhang2011", "undercoverkanye")

r_peeps <- c("hadleywickham", "JennyBryan", "robinson_es")

request(rohe_lab, neighborhood = TRUE)
```

`twittercache` is really built to enable to BFS type searches through the twitter graph. If you want to add known about all the nodes in the neighborhood of a single node, use:

```{r}
request("alexpghayes", neighborhood = TRUE)
```

I recommend against asking for the neighborhood huge accounts, because `twittercache` considers both friends and followers part of the neighborhood, and so sampling will take forever if you do things like:

```{r eval = FALSE}
request("hadleywickham", neighborhood = TRUE)
```

`request()` *does not* do any sampling. It just builds a list of nodes that need to be sampled. `request()` is smart:

- If a node is already in the cache, it isn't added to the queue
- Redundant nodes are not added to the queue

If you request information on a Twitter user that doesn't exist, you'll get a warning:

```{r}
request("not_a_real_twitter_handle")
```

To see the current list of requests, use 

```{r}
get_requests()
```

This returns a character vector of user IDs. It's mostly for internal use at the moment and I might write a nicer wrapper around it that returns screen names at some point.

To clear the current requests, use

```{r}
clear_requests()
```

## Step 3: Sample nodes!

All you need to do is run

```{r}
sample_twitter_graph()
```

For more verbose output, use

```{r}
library(logger)

log_level(DEBUG)

sample_twitter_graph()
```

If someone knows better practices for logging things, please reach out, I really have no clue what I'm doing here.

On occasion `rtweet()` or the Twitter API will just explode and won't be able to sample a node. `sample_twitter_graph()` records these failures and moves on to the next requested node in cases like this.

To see nodes that `sample_twitter_graph()` managed to sample, run

```{r}
get_failures()
```

which again returns a character vector of user IDs.

In general, `sample_twitter_graph()` is designed to be pretty robust. If it crashes the samples you already got are already saved into the cache so you don't lose work, and if you run it again it'll update the request list and make sure not to repeat any work.

## Step 4: Export the cache

export the cache / import the cache

TODO

## Frequently asked questions

**How do you manage the API rate limits?**

Currently we just sample one node a minute. This complies with the Twitter API rate limits but is a bit dicey. Improving this is a priority.

**Where is the cache itself?**

It's at `~/.twittergraph/`.

**This whole cache thing is a bad idea**

Probably, but it works for me.

**What about users with big follower counts? Do you sample all the followers?**

No. We only sample up to 5,000 friends and 5,000 followers. This is mostly because I'm lazy and also it's wasteful to spend API calls on someone with tons of followers.

Recall that you can pick up an edge in the network from either node. We recommend trying to make sure the node with smaller degree is in your sample.

**What happens when I try to sample protected users?**

We remove these users from the sample at export time.

  
## TODO
- just put create_cache_if_needed in user facing functions, and nowhere else
- add move `force` argument from `visit` to `request`
